PAMELA: an annotation-based Java Modeling Framework

### 2022-03-10 main.tex
tex names standardization
Updates from Overleaf

\input{2-Abstract}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

%\section{Industrial experimentation and validation}
%\label{sec:validation}
%\input{validation.tex}

\input{6-Experimentations}
\label{sec:Experimentations}

@@

%\input{4-ApproachOverview}

%\input{5-Features}

%\input{6-Experimentations}

%\input{7-Relatedworks}

\input{8-Conclusion}

>>>>

\input{abstract}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\clearpage
\section*{Software and Code Metadata}
\label{}

\section*{Current executable software version}
\label{}

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(executable) Software metadata description} &  \\
\hline
S1 & Current software version & 1.5 \\
\hline
S2 & Permanent link to executables of this version  & https://maven.openflexo.org/artifactory/
libs-release/org/openflexo/pamela-core/1.5 \\
\hline
S3 & Legal Software License & Dual licencing: GPLV3 and EUPL \\
\hline
S4 & Computing platform/Operating System & Java runtime environment \\
\hline
S5 & Installation requirements \& dependencies & JRE \geq 1.6\\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & https://pamela.openflexo.org\\
\hline
S7 & Support email for questions & contact@openflexo.org\\
\hline
\end{tabular}
\caption{Software metadata}
\label{} 
\end{table}

\section*{Current code version}
\label{}

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} &  \\
\hline
C1 & Current code version & 1.6.1 \\
\hline
C2 & Permanent link to code/repository used of this code version & https://github.com/openflexo-team/pamela \\
\hline
C3 & Legal Code License   & Dual licencing: GPLV3 and EUPL \\
\hline
C4 & Code versioning system used & git / github \\
\hline
C5 & Software code languages, tools, and services used & Java \\
\hline
C6 & Compilation requirements, operating environments \& dependencies & JDK \geq 1.6\\
\hline
C7 & If available Link to developer documentation/manual & https://pamela.openflexo.org \\
\hline
C8 & Support email for questions & contact@openflexo.org\\
\hline
\end{tabular}
\caption{Code metadata}
\label{} 
\end{table}

@@

\input{experimentations}
\label{sec:Experimentations}

@@

\input{conclusion}
